article

### 2015-12-24 article.rmd
Functional, added pairs just for testing.

```{r, echo=FALSE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", ""),
                          submitButton("Plot!"),
                          plotOutput("plot")
                          )
        ))
        server <- function(input, output, session) {
                output$plot<-renderPlot({
                        f<-function(x) {eval(parse(text=input$filtering))}
                        x<-1:10
                        plot(x,f(x))
                }                        
                )              
        }

>>>>

```{r, echo=TRUE}
        ui <- shinyUI(fluidPage(
                mainPanel(textInput("filtering", "FTS Filter:", ""),
                          submitButton("Plot!"),
                          plotOutput("plot")
                          )
        ))
        server <- function(input, output, session) {
                output$plot<-renderPlot({
                        f<-function(x) {as.character(input$filtering)}

                        sql <- paste("SELECT sourceTable, sum(scoreBoolean), sum(scoreQE),
        max(scoreBoolean),max(scoreQE),
        avg(scoreBoolean), avg(scoreQE),
        avg(lengthContent),
        avg(scoreQE) / count(sourceTable) as weight,
        count(sourceTable)
FROM
(
SELECT \"BC\" as sourceTable, FTS_DOC_ID, match(BC.content) against (\"" ,f(x) ," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BC.content) against (\""  ,f(x), "\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContent BC
WHERE
  match(BC.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
UNION
SELECT \"BL\" as sourceTable, FTS_DOC_ID, match(BL.content) against (\"",f(x)," \" IN BOOLEAN MODE) as scoreBoolean,
       match(BL.content) against (\"" ,f(x)," \" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION) scoreQE,
       length(content) as lengthContent
FROM
        bookContentByLine BL
WHERE
  match(BL.content) against (\"", f(x) ,"\" IN NATURAL LANGUAGE MODE WITH QUERY EXPANSION)
) unionTable
GROUP BY sourceTable
;" , sep = "")
                        rs <- dbGetQuery(con, sql)
                        #rs
                        #x<-1:10

                        #pairs(rs$sourceTable + rs$weight, data = rs)
                        pairs(rs[,2:10])
                        # plot(x,f(x))
                }                        
                )              
        }
